Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-31 paper-for_arxiv/paper.tex
adding SFI to acknowledgements
adding Ryan James to the ack. for help with TE code

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.

>>>>

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset, and Ryan James for their valuable comments and suggestions. Finally, we would like to acknowledge the Santa Fe Institute, where this project began\alert{not sure how to word this last sentence}.
